Voter Characteristics and Political Support in the US

### 2024-03-16 paper/paper.qmd
Inline citation for code

```{r}
#| echo: false
#| message: false
#| label: tmp-label1
#| tbl-cap: tmp-caption1

ces2020 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| label: tmp-label2
#| tbl-cap: tmp-caption2

ces2020 |>
  ggplot(aes(x = gun_ownership, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Gun Ownership",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev, labels = label_wrap(10)) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-gender
#| fig-cap: "Predicted support of Biden given gender vs. actual support"
political_predictions |>
  mutate(gender = factor(gender)) |>
  ggplot(aes(x = gender, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Gender",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-race
#| fig-cap: "Predicted support of Biden given race vs. actual support"
political_predictions |>
  mutate(race = factor(race)) |>
  ggplot(aes(x = race, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Race",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-gun-owner
#| fig-cap: "Predicted support of Biden given gun ownership vs. actual support"
political_predictions |>
  mutate(gun_ownership = factor(gun_ownership)) |>
  ggplot(aes(x = gun_ownership, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Gun Ownership",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

>>>>

```{r}
#| echo: false
#| message: false
#| label: tmp-label1
#| tbl-cap: tmp-caption1
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| label: tmp-label2
#| tbl-cap: tmp-caption2
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = gun_ownership, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Gun Ownership",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev, labels = label_wrap(10)) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-gender
#| fig-cap: "Predicted support of Biden given gender vs. actual support"

# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
political_predictions |>
  mutate(gender = factor(gender)) |>
  ggplot(aes(x = gender, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Gender",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-race
#| fig-cap: "Predicted support of Biden given race vs. actual support"

# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
political_predictions |>
  mutate(race = factor(race)) |>
  ggplot(aes(x = race, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Race",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-model-gun-owner
#| fig-cap: "Predicted support of Biden given gun ownership vs. actual support"

# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
political_predictions |>
  mutate(gun_ownership = factor(gun_ownership)) |>
  ggplot(aes(x = gun_ownership, y = estimate, color = voted_for)) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs(
    x = "Gun Ownership",
    y = "Estimated probability that an \n individual voted for Biden",
    color = "Candidate actually voted for"
  ) +
  theme_classic() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```
